---
title: 'Results for NEJM SPRINT Challenge'
author: "Himes Lab"
date: Feb 14, 2017
output:
  html_document:
    toc: TRUE 
    depth: 3 
    theme: paper 
    highlight: tango
---

***


```{r eval=TRUE, echo=FALSE, message=FALSE,warning=FALSE}
### load library ###
library(ggplot2)
library(pander)
library(reshape2)
library(data.table)
library(survival)
library(forestplot)
library(ggfortify)
```


```{r set-options, echo=FALSE, cache=FALSE}
options(width = 400)
```  

## Data from SPRINT
* Original information:
    + Baseline measurement for stuey participants: baseline.csv
    + Occurance of clinical outcomes during treatment: outcomes.csv
    + Occurance of serious adverse events during treatment: safety.csv
    + Blood pressure measured in each visit points duringn clinical trial course: bp.csv
    
```{r eval=F, echo=FALSE, message=FALSE}
baseline <- read.csv("data/baseline.csv") # study participants
baseline$INTENSIVE <- as.factor(baseline$INTENSIVE)
levels(baseline$INTENSIVE) <- c("STANDARD","INTENSIVE")
baseline$FEMALE <- as.factor(baseline$FEMALE)
levels(baseline$FEMALE) <- c("MALE","FEMALE")
baseline$SUB_SENIOR <- as.factor(baseline$SUB_SENIOR)
levels(baseline$SUB_SENIOR) <- c("<75yr",">=75yr")
outcomes <- read.csv("data/outcomes.csv")
safety <- read.csv("data/safety.csv")
dat <- Reduce(function(x, y) merge(x, y, by="MASKID", all=TRUE), list(baseline,outcomes,safety))
```

```{r eval=TRUE, echo=FALSE, message=FALSE}
### Import data ###
dat <- read.csv("intermediate/SPRINT.csv")
bp <- read.csv("intermediate/bp.csv")
SBP_5yr <- read.csv("intermediate/SBP_5yr.csv")
datbp_all <- merge(SBP_5yr,dat,by=c("MASKID"),all.x=TRUE)
```


## Replication results from NEJM paper

### Figure2: SBP over the course of the trial


```{r eval=TRUE, echo=FALSE, message=FALSE}
bptime <- bp
bptime$INTENSIVE <- as.factor(bptime$INTENSIVE)
levels(bptime$INTENSIVE) <- c("STANDARD","INTENSIVE")
setDT(bptime)
bp_ct <- bptime[,list(mean=mean(SBP),sd=sd(SBP),n=length(SBP)),by=c("INTENSIVE","visitcode2")]
bp_ct$error_norm <- qnorm(0.975)*bp_ct$sd/sqrt(bp_ct$n)
bp_ct$error_t <- qt(0.975,df=bp_ct$n-1)*bp_ct$sd/sqrt(bp_ct$n)
# plot
plot <- ggplot(bp_ct,aes(x=visitcode2,y=mean,colour=INTENSIVE,group=INTENSIVE,fill=INTENSIVE))+geom_point()+geom_line()+geom_errorbar(aes(ymax=mean+error_norm, ymin=mean-error_norm), width=0.2) + scale_x_continuous(breaks=seq(0,60,6)) +scale_y_continuous(limits=c(110,150)) + xlab("Visit Month") + ylab("SBP") + theme(
  panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  legend.position = "bottom",
  axis.line = element_line(colour = "black")
  )
plot
```

## Distribution of mean and median trial SBP

```{r eval=TRUE, echo=FALSE, message=FALSE, fig.width=5,fig.height=4}
ggplot(data=SBP_5yr,aes(x=mean))+ geom_histogram(aes(y=..density..),binwidth=5,colour="black",fill="white") + geom_density(alpha=.2, fill="#FF6666") + theme(legend.title=element_blank()) + xlab("Mean trial SBP") 
ggplot(data=SBP_5yr,aes(x=median)) + geom_histogram(aes(y=..density..),binwidth=5,colour="black",fill="white") + geom_density(alpha=.2, fill="#FF6666") + theme(legend.title=element_blank()) + xlab("Median trial SBP") 
```

## Cox proportional hazard ratio of death and primary outcomes in spline models

### Death outcome
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
fit <- coxph(Surv(T_DEATH,EVENT_DEATH)~pspline(median,df=4),data=datbp_all)
termplot(fit,se=TRUE,rug=TRUE,xlab="Median trial SBP",ylab="Log(Hazard ratio)",terms=1)
```

### Primary outcome
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
fit <- coxph(Surv(T_PRIMARY,EVENT_PRIMARY)~pspline(median,df=4),data=datbp_all)
termplot(fit,se=TRUE,rug=TRUE,xlab="Median trial SBP",ylab="Log(Hazard ratio)",terms=1)
```

### Primary or death outcome
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
fit <- coxph(Surv(T_PRIMARYORDEATH,EVENT_PRIMARYORDEATH)~pspline(median,df=4),data=datbp_all)
termplot(fit,se=TRUE,rug=TRUE,xlab="Median trial SBP",ylab="Log(Hazard ratio)",terms=1)
```

## Cox proportional hazard ratio in SBP groups

```{r eval=TRUE, echo=FALSE, message=FALSE}
### Function used in this section ###
subctHR <- function(dt,x,covars) { # x: event name. Will add "EVENT_" for event coding and "T_" for time coding; covars: covariates in survival model. Put the one of interest (e.g. SBP) as the first one
  if (length(covars)==1) {covarexp <- covars} else {covarexp <- paste(covars,collapse="+")}
  if (grepl("SAE|ERS|MCE|OHO",x)){
    event <- paste0(x,"_EVNT")
    time <- paste0(x,"_DAYS")
  } else {
    event <- paste0("EVENT_",x)
    time <- paste0("T_",x)
  }
  form <- as.formula(paste0("Surv(",time,",",event,")~",covarexp))
  # get the variable of interest
  invar <- covars[1]
  # remove missingness
  dt <- dt[!(is.na(dt[,invar])),]
  # compute HR for each subgroup
  res <- summary(coxph(form,data=dt))
  # get all the variable names of survival results
  row_names <- row.names(res$coefficients)
  # get names of the variable of interest
  invar_names <- row_names[grep(invar,row_names)]
  # create reference group
  refname <- unique(dt[,invar])[which(!unique(dt[,invar])%in%sub(invar,"",invar_names))]
  HR.CI <- 1
  pval<- NA
  HR <- 1
  upperCI <- 1
  lowerCI <- 1
  ct <- dt[which(dt[,invar]==refname),c(event,invar,"INTENSIVE")]
  nevent <- sum(ct[,event])
  ntotal <- length(ct[,event])
  prop <- round(nevent/ntotal*100,2)
  nintarm <- length(ct[which(ct$INTENSIVE=="INTENSIVE"),event])
  propintarm <- round(nintarm/ntotal*100,2)
  sample <- paste0(nevent,"/",ntotal,"(",prop,")")
  sampintarm <- paste0(nintarm,"/",ntotal,"(",propintarm,")")
  out <- data.frame(group=refname,sample,intensive_arm=sampintarm,HR.CI,pval,HR,upperCI,lowerCI)
  for (i in 1:length(invar_names)) {
    sub_coef <- res$coefficients[i,]
    pval <- unname(sub_coef[5])
    sub_conf <- res$conf.int[i,]
    HR <- unname(sub_conf[1])
    lowerCI <- unname(sub_conf[3])
    upperCI <- unname(sub_conf[4])
    HR.CI <- paste0(round(HR,2),"(",round(lowerCI,2),"-",round(upperCI,2),")")
    name <- invar_names[i]
    group <- sub(invar,"",name) # replace first string
    # count number in each subgroups
    ct <- dt[which(dt[,invar]==group),c(event,invar,"INTENSIVE")]
    nevent <- sum(ct[,event])
    ntotal <- length(ct[,event])
    prop <- round(nevent/ntotal*100,2)
    nintarm <- length(ct[which(ct$INTENSIVE=="INTENSIVE"),event])
    propintarm <- round(nintarm/ntotal*100,2)
    sample <- paste0(nevent,"/",ntotal,"(",prop,")")
    sampintarm <- paste0(nintarm,"/",ntotal,"(",propintarm,")")
    out <- rbind(out,data.frame(group,sample,intensive_arm=sampintarm,HR.CI,pval,HR,upperCI,lowerCI))
  }
  out$pval <- ifelse(out$pval>=0.01,round(out$pval,2),format(out$pval,digits=3))
  return(out)
}
```

```{r eval=TRUE, echo=FALSE, message=FALSE}
forplot <- function(dt){
  if ("HR"%in%names(dt)) {risk <- "HR"} else if ("OR"%in%names(dt)) {risk <- "OR"}
  riskcomb <- paste0(risk,".CI")
  ctplot <- dt[,c("group","sample","intensive_arm",riskcomb)]
  names(ctplot)[3] <- "riskcomb"
  HRplot <- dt[,c(risk,"upperCI","lowerCI")]
  ctplot[,names(ctplot)] <- sapply(ctplot[, names(ctplot)], as.character)
  rowname1 <- c(group=" ",sample="Event/Total",pval="Intensive arm/Total",riskcomb=" ")
  rowname2 <- c(group="Group",sample="Counts(%)",pval="Counts(%)",riskcomb=paste0(risk,"(95% CI)"))
  data1 <- rbind(rowname2,ctplot)
  ctplot <- rbind(rowname1,data1)
  ctplot <- ctplot[,c(1,4)] # 0.5
  #ctplot <- ctplot[,2:4] # 0.3
  m <- c(NA,NA,round(HRplot[,1],2))
  l <- c(NA,NA,round(HRplot$lowerCI,2))
  u <- c(NA,NA,round(HRplot$upperCI,2))
  min <- min(l,na.rm=TRUE)
  max <- max(u,na.rm=TRUE)
  # assign the ticks for x-axis, or will get into trouble
  if(floor(min)==0){start=0.5}else{start=floor(min)}
  if(ceiling(max)>=2.5){end=2.5}else{end=ceiling(max)}
  #plot <- forestplot(ctplot,m,l,u,clip=c(0.5,2.5),xlog=TRUE,graphwidth=unit(c(0.15,0),"npc"),xticks = seq(start,end,by=0.5),txt_gp=fpTxtGp(label=list(gpar(cex=0.7)),ticks = gpar(cex=0.7)),new_page=FALSE,boxsize=0.15) # graphwidth (range for CI, 1-start point for CI), ,graphwidth=unit(c(0.35,0),"npc"); colgap (gap between texttable and plot; width range of plot) ,colgap=unit(c(0,0.2),"npc")
  plot <- forestplot(ctplot,m,l,u,clip=c(0.5,2.5),xlog=TRUE,graphwidth=unit(c(0.5,0),"npc"),xticks = c(0.75,1,2,3,4),txt_gp=fpTxtGp(label=list(gpar(cex=0.5)),ticks = gpar(cex=0.5)),boxsize=0.12)
}

```

### Parition into three SBP groups <115 mmHg, 115-140 mmHg, >140 mmHg
#### Death outcome
```{r eval=T, echo=FALSE, message=FALSE}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
orglev <- levels(SBP_all$medianpar)
# make the second group as reference group
SBP_all <- within(SBP_all,medianpar<- relevel(medianpar,ref=2))
ctHR <- subctHR(SBP_all,"DEATH","medianpar")
ctHR$group <- factor(ctHR$group, levels=orglev)
ctHR <- ctHR[order(ctHR$group),]
ctHR$group <- c("<115 mmHg","115-140 mmHg",">140 mmHg")
ctHR_death3 <- ctHR

tb <- ctHR_death3
row.names(tb) <- NULL
colnames(tb) <- c("group","Event/Total(%)","Intensive arm/Total(%)","HR (95%CI)","P value")
pander(tb[,1:5])
```

#### Primary outcome
```{r eval=T, echo=FALSE, message=FALSE}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
orglev <- levels(SBP_all$medianpar)
# make the second group as reference group
SBP_all <- within(SBP_all,medianpar<- relevel(medianpar,ref=2))
ctHR <- subctHR(SBP_all,"PRIMARY","medianpar")
ctHR$group <- factor(ctHR$group, levels=orglev)
ctHR <- ctHR[order(ctHR$group),]
ctHR$group <- c("<115 mmHg","115-140 mmHg",">140 mmHg")
ctHR_primary3 <- ctHR

tb <- ctHR_primary3
row.names(tb) <- NULL
colnames(tb) <- c("group","Event/Total(%)","Intensive arm/Total(%)","HR (95%CI)","P value")
pander(tb[,1:5])
```


### Parition into four SBP groups <115 mmHg, 115-130 mmHg, 130  >140 mmHg
#### Death outcome
```{r eval=TRUE, echo=FALSE, message=FALSE}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,130,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
orglev <- levels(SBP_all$medianpar)
# make the second group as reference group
SBP_all <- within(SBP_all,medianpar<- relevel(medianpar,ref=2))
ctHR <- subctHR(SBP_all,"DEATH","medianpar")
ctHR$group <- factor(ctHR$group, levels=orglev)
ctHR <- ctHR[order(ctHR$group),]
ctHR$group <- c("<115 mmHg","115-130 mmHg", "131-140 mmHg",">140 mmHg")
ctHR_death4 <- ctHR

tb <- ctHR_death4
row.names(tb) <- NULL
colnames(tb) <- c("group","Event/Total(%)","Intensive arm/Total(%)","HR (95%CI)","P value")
pander(tb[,1:5])
```

#### Primary outcome
```{r eval=TRUE, echo=FALSE, message=FALSE}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,130,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
orglev <- levels(SBP_all$medianpar)
# make the second group as reference group
SBP_all <- within(SBP_all,medianpar<- relevel(medianpar,ref=2))
ctHR <- subctHR(SBP_all,"PRIMARY","medianpar")
ctHR$group <- factor(ctHR$group, levels=orglev)
ctHR <- ctHR[order(ctHR$group),]
ctHR$group <-c("<115 mmHg","115-130 mmHg", "131-140 mmHg",">140 mmHg")
ctHR_primary4 <- ctHR

tb <- ctHR_primary4
row.names(tb) <- NULL
colnames(tb) <- c("group","Event/Total(%)","Intensive arm/Total(%)","HR (95%CI)","P value")
pander(tb[,1:5])
```

## Cumulative hazard proportion
### Death outcome
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
fit <- survfit(Surv(T_DEATH,EVENT_DEATH)~medianpar,data=SBP_all)

# NOTE: "#F8766D" (red) "#00BA38" (green)  "#619CFF" (blue)
plot <- autoplot(fit,fun="event",conf.int.fill=NULL, surv.linetype=1,surv.size=0.5,censor=FALSE,xlim=c(0,1825)) + xlab("Years") + ylab("Cumulative hazard") + scale_x_continuous(expand=c(0,0),limits=c(0,1900),breaks=c(365,730,1095,1460,1825),labels=c(1:5)) +
  scale_y_continuous(expand=c(0,0),limits=c(0,0.13),breaks=seq(0,0.12,0.02)) +
  theme(
  panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"),
  legend.title=element_blank(),legend.position="none"
  #axis.title=element_text(size=8.5),
  #axis.text=element_text(size=8),
  #axis.ticks=element_line(size=0.5)
  ) + 
  annotate("text", x=1600, y=0.067, label= "<115 mmHg", color="#619CFF") +
  annotate("text", x=1570, y=0.03, label= "115-140 mmHg", color="#F8766D") +
  annotate("text", x=1600, y=0.12, label= ">140 mmHg", color="#00BA38")
plot
```

### Primary outcome
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
fit <- survfit(Surv(T_PRIMARY,EVENT_PRIMARY)~medianpar,data=SBP_all)

# NOTE: "#F8766D" (red) "#00BA38" (green)  "#619CFF" (blue)
plot <- autoplot(fit,fun="event",conf.int.fill=NULL, surv.linetype=1,surv.size=0.5,censor=FALSE,xlim=c(0,1825)) + xlab("Years") + ylab("Cumulative hazard") + scale_x_continuous(expand=c(0,0),limits=c(0,1900),breaks=c(365,730,1095,1460,1825),labels=c(1:5)) +
  scale_y_continuous(expand=c(0,0),limits=c(0,0.13),breaks=seq(0,0.12,0.02)) +
  theme(
  panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"),
  legend.title=element_blank(),legend.position="none"
  #axis.title=element_text(size=8.5),
  #axis.text=element_text(size=8),
  #axis.ticks=element_line(size=0.5)
  ) + 
  annotate("text", x=1600, y=0.053, label= "<115 mmHg", color="#619CFF") +
  annotate("text", x=1570, y=0.080, label= "115-140 mmHg", color="#F8766D") +
  annotate("text", x=1600, y=0.110, label= ">140 mmHg", color="#00BA38")
plot
```


## Cox proportional hazard ratio of SAEs in spline model


```{r eval=TRUE, echo=FALSE, message=FALSE}
spSAEplot <- function(dt,x,covars,main) {
  event <- paste0(x,"_EVNT")
  time <- paste0(x,"_DAYS")
  covar <- covars[1]
  spvar <- paste0("pspline(",covars[1],",df=4)")
  if (length(covars)==1) {
    covarexp <- spvar
    main <- main
  } else {
      covarexp <- paste(c(spvar,covars[2:length(covars)]),collapse="+")
      main <- paste0(main, " adjusted for ", paste(covars[-1],collapse=","))
  }
  form <- as.formula(paste0("Surv(",time,",",event,")~",covarexp))
  fit <- coxph(form,data=dt)
  termplot(fit,se=TRUE,rug=TRUE,xlab="Median trial SBP",ylab="Log(Hazard ratio)",terms=1,main=main)
}
```


### Total SAE
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
spSAEplot(SBP_all,"SAE","median",main="")
```

Use the <115 mmHg, 115-140 mmHg and 140 mmHg as partition groups

```{r eval=TRUE, echo=FALSE, message=FALSE}
SBP_all <- datbp_all
pts <- c(min(SBP_all$median),114,140,max(SBP_all$median))
SBP_all$medianpar <- cut(SBP_all$median,pts,include.lowest=TRUE)
orglev <- levels(SBP_all$medianpar)
# make the second group as reference group
SBP_all <- within(SBP_all,medianpar<- relevel(medianpar,ref=2))
ctHR <- subctHR(SBP_all,"SAE","medianpar")
ctHR$group <- factor(ctHR$group, levels=orglev)
ctHR <- ctHR[order(ctHR$group),]
ctHR$group <- c("<115 mmHg","115-140 mmHg",">140 mmHg")
ctHR_SAE3 <- ctHR

tb <- ctHR_SAE3
row.names(tb) <- NULL
colnames(tb) <- c("group","Event/Total(%)","Intensive arm/Total(%)","HR (95%CI)","P value")
pander(tb[,1:5])
```
### Other SAEs
```{r eval=TRUE, echo=FALSE, message=FALSE,fig.width=5,fig.height=4}
x <- c("REL_SAE", "HYP_SAE", "SYN_SAE", "BRA_SAE", "ELE_SAE", "INJ_SAE", "AKI_SAE", "HYP_ERS", "SYN_ERS", "BRA_ERS", "ELE_ERS","INJ_ERS", "AKI_ERS", "LON_MCE", "HIN_MCE", "LOK_MCE", "HIK_MCE", "ALO_OHO", "WDZ_OHO")
names <- c("RelatedSAE","Hypotension","Syncope","Bradycardia","ElectrolyteAbnormality","InjuriousFall","AcuteKindeyInjuryORRentalFailure","Hypotension_ER","Syncope_ER","Bradycardia_ER","ElectrolyteAbnormality_ER","InjuriousFall_ER","AcuteKindeyInjuryORRentalFailure_ER","LowSodium","HighSodium","LowPotassium","HighPotassium","OrthostaticHypotensionNODizziness","OrthostaticHypotensionWithDizziness")
for (i in 1:length(x)) {
  spSAEplot(SBP_all,x[i],"median",names[i])
}
```

